Verifying Demonstrations

### 2018-11-30 paper/protocol.tex
adds references to appendices
integrating trust assumptions in the body of the paper

We now present \CROCUS, a protocol for privately verifiable crowd counts.
The protocol consists of three phases:
before the protest, with the setup and registration steps (\cref{ProtocolSetup});
during the protest, with the creation, join, participation, and submission 
steps (\cref{ProtocolDuring});
and after the protest, with the verification step (in
\cref{ProtocolVerification}). Note that some of the figures with
protocol minutiae from related work are in~\cref{anon-cred-figures}.

@@

\emph{Setup: \((\spk, \ssk)\gets \CROCUSsetup\).}
During the setup phase, the \ac{CA} creates all the needed keys.
The \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\gets 
  \ACsetup\) (see \cref{ACsignAlg}).

@@

The protester sends \(\pid\) to the witness.
Then they run the protocol \[
  \Proto{\ACproveSig[\spk, k, r, \sigma]}{\ACverifySig[\spk, \ssk]}
\] (see \cref{ACacAlg}).
Note that the \ac{PK} in \cref{ACacAlg} must be run as \iac{PPK}.
If the protocol succeeds, the witness will compute \(\wid \gets 
  \ACprf[_{\sk_W}][\pid]\) and send \((\wid, t_s', l)\) to the protester.

>>>>

We now present \CROCUS, a protocol for privately verifiable crowd counts.
The protocol consists of three phases:
before the protest, with the setup and registration steps (\cref{ProtocolSetup}),
during the protest, with the creation, join, participation, and submission steps (\cref{ProtocolDuring})
and after the protest, with the verification step (in
\cref{ProtocolVerification}). Note that some of the figures with
protocol minutiae from related work are in~\cref{anon-cred-figures}.

@@

\emph{Setup: \((\spk, \ssk)\gets \CROCUSsetup\).}

During the setup phase, the \ac{CA} creates all the needed keys.
The \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\gets 
  \ACsetup\) (see \cref{ACsignAlg}).

@@

The protester sends \(\pid\) to the witness.
Then they run the protocol \(\Proto{\ACproveSig[\spk, k, r, 
    \sigma]}{\ACverifySig[\spk, \ssk]}\) (see \cref{ACacAlg}).
Note that the \ac{PK} in \cref{ACacAlg} must be run as \iac{PPK}.
If the protocol succeeds, the witness will compute \(\wid \gets 
  \ACprf[_{\sk_W}][\pid]\) and send \((\wid, t_s', l)\) to the protester.
